\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-19 intro.tex
minor edits
update in intro

We have found that checking high-level specifications is necessary but not sufficient, due to the gap between the specification and the executable code.
%that ultimately powers the distributed systems.
Our goal is to bridge this gap. We propose a new framework that
applies verification techniques for high-level specifications directly
to the executable code. Our framework is different from prior
approaches where the developers were required to either switch to an
unfamiliar special programming language~\ref{}, or manually annotate
and instrument code~\ref{}. Instead, we allow developers to test
{\em unmodified production code} by writing test harnesses in a
mainstream programming language. This
significantly lowered the acceptance barrier for adoption by the
Microsoft Azure team.

%We present a new method for testing an implementation of a distributed system and uncovering bugs before the system is released in the wild.
Our framework is based on \psharp~\cite{deligiannis2015psharp}, an extension of the mainstream language \csharp that provides support for modeling, specification, and systematic testing of asynchronous systems.
To test a distributed system with the \psharp framework, the programmer augments the system code with three artifacts -- a model of the nondeterministic execution environment of the system, a concurrent test harness that drives the system towards interesting behaviors, and safety or liveness specifications.
The \psharp systematic testing engine then systematically explores all behaviors exercised by the test harness and validates them against the provided specifications.

We have applied our framework to three distributed storage systems in Microsoft Azure: Azure Storage vNext, Azure Table Live Migration, 
and Azure Service Fabric.
%a distributed storage system; a system for migrating data across partitions; and a big-data computing system.
We uncovered numerous bugs in these systems, including, most notably, a subtle liveness bug that only intermittently 
manifested during stress testing for months without being fixed.
Our testing approach uncovered this bug in a very small setting, which made it easy to examine traces, identify, and eventually fix the problem.
Our experience demonstrates that bugs in production do not need a large setting to be reproduced;
they can be reproduced in small settings with easy to understand traces.

>>>>

We have found that checking high-level specifications is necessary but not sufficient, due to the gap between the specification and the executable code. Our goal is to bridge this gap. We propose a new framework that validates high-level specifications directly on the executable code. Our framework is different from prior approaches that required developers to either switch to an unfamiliar domain specific language~\cite{killian2007life, desai2015building}, or manually annotate and instrument their code~\cite{}. Instead, we allow developers to test \emph{unmodified production code} by writing test harnesses in \csharp, a mainstream programming language. This significantly lowered the acceptance barrier for adoption by the Microsoft Azure team.

%We present a new method for testing an implementation of a distributed system and uncovering bugs before the system is released in the wild.
Our framework is based on \psharp~\cite{deligiannis2015psharp}, an extension of \csharp that provides support for modeling, specification, and systematic testing of distributed systems written in Microsoft's .NET framework.
To test a distributed system with \psharp, the programmer augments the original system code with three artifacts -- a model of the nondeterministic execution environment of the system, a concurrent test harness that drives the system towards interesting behaviors, and safety or liveness specifications.
The \psharp testing engine then systematically explores all behaviors exercised by the test harness and validates them against the provided specifications.

We have applied \psharp to three distributed storage systems in Microsoft Azure: Azure Storage vNext, Azure Table Live Migration, and Azure Service Fabric.
%a distributed storage system; a system for migrating data across partitions; and a big-data computing system.
We uncovered numerous bugs in these systems, including, most notably, a subtle liveness bug that only intermittently 
manifested during stress testing for months without being fixed.
Our testing approach uncovered this bug in a very small setting, which made it easy to examine traces, identify, and eventually fix the problem.
Our experience demonstrates that bugs in production do not need a large setting to be reproduced;
they can be reproduced in small settings with easy to understand traces.
